Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-10 longoutput.tex
Write more about H prop

Then, we ensure that the gates are applied correctly.
$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
Extra care must be taken for boundary cases.
$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$

I probably need to explain why this works but TODO I'll leave it for another day.

Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
So we can write
$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$

>>>>

Then, we ensure that the gates are applied correctly.
$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$

It is easier to check that it works and is Hermitian and works as expected by a unitary change of basis.

$$W=\sum_{j=0}^L U_j\ldots U_1\otimes\ket{j}\bra{j}$$
$$W^\dagger\phi=\sum_{t=0}^T\ket{x}\otimes\ket{\hat{t}}$$
$$W^\dagger H_{prop} W=
\begin{pmatrix}
	\frac{1}{2} & -\frac{1}{2} & & & &  \\
	-\frac{1}{2} & 1 & -\frac{1}{2} & & & \\
	& -\frac{1}{2} & 1 & \ddots & & \\
	& & \ddots & \ddots & -\frac{1}{2} & \\
	& & & -\frac{1}{2} & 1 & -\frac{1}{2} \\
	& & & & -\frac{1}{2} & \frac{1}{2}
\end{pmatrix}$$

I probably need to say even more on why this works but TODO I'll leave it for another day. There's also a closed form to the second smallest eigenvalue above that is apparently related to random walks but I can't find the source at the moment.

Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
So we can write
$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
Extra care must be taken for boundary cases.
$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
